---
title: "How to use Mysterycoffee?"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## The idea behind Mysterycoffee

With working from home, some of the serendipity was taken out of the work day: how about those chance meetings at the water cooler or the coffee machine?

Mysterycoffee was created to fill this void: by randomly pairing colleagues and inviting them for a shared coffee break, those magical moments can happen again!

First, load the package:
```{r setup}
library(mysterycoffee)
```

Then, create a list of your colleagues, as a vector:

```{r}
colleagues <- c("Anna", "Bart", "Christine", "Don", "Elise", "Frank")
```

Pair the colleagues, using `make_groups`:
```{r usage example}
make_groups(colleagues)

```

You can even assign a time slot, as follows:

```{r usage with time}
# make_groups_by_time(colleagues)
```

That's it! 
